Effectful Semantics for Substructural SSA

### 2023-11-13 pldi24/paper.tex
Tap

\TODO{ssec:separation}

@@

\TODO{segue to separation logic}

Building on the ideas in \cite{mellies-ftrs}, we will show how a simple separation logic based on \cite{reynolds-separation-2002} slightly adapted to the categorical setting gives us a very rich \isotopessa model supporting a basic notion of refinement types, while at the same time giving us a nontrivial notion of nonlinear types.

@@

\TODO{equality vs \cite{mellies-ftrs}}
\TODO{sliding w/ properly restricted equality}
\TODO{\(\implies\) central = no printing, heap allowed: can make heap operations relevant/affine too!}

>>>>

\label{ssec:separation}

@@

We can use this construction to, building on the ideas in \cite{mellies-ftrs}, show how a simple separation logic based on \cite{reynolds-separation-2002} slightly adapted to the categorical setting gives us a very rich \isotopessa model supporting a basic notion of refinement types, while at the same time giving us a nontrivial notion of nonlinear types.

@@

We can clearly see that this is a refinement type system in the sence of \cite{mellies-ftrs}: in particular, there is a forgetful functor \((A, \Phi) \mapsto A\) which is simply the identity on morphisms. Unfortunately, this means that our notion of equality is a little too stringent, since we need to consider equality on inputs which do not match our preconditions.

\TODO{example, + example set}

\TODO{restricted equality}

\TODO{sliding w/ properly restricted equality}

\TODO{\(\implies\) central = no printing, heap allowed: can make heap operations relevant/affine too!}
